On the Limitations of Weighted Model Counting

### 2020-03-28 paper.tex
Update a lemma into a stronger result

% TODO: maybe I can rephrase this into a stronger result specifically about
% a /\ ~p. Do I even want to do that?
\begin{lemma}
  Let $(p)$ be a principal ideal. For any $a, b \in \mathbf{B}$, $a/(p) \le
  b/(p)$ if and only if there exist $a', b' \in \mathbf{B}$ such that $a'/(p) =
  a/(p)$, $b'/(p) = b/(p)$, and $a' \le b'$.
\end{lemma}
\begin{proof}
  Let us begin with the `only of' direction, and let $f\colon \mathbf{B} \to
  \mathbf{B}/(p)$ be defined as $f(x) = x/(p)$. If $a' \le b'$, then $f(a') \le
  f(b')$ by \cref{lemma:canonical_homomorphism,lemma:homomorphisms_and_order}.
  Thus $a'/(p) \le b'/(p)$, and $a/(p) \le b/(p)$ as required.

  For the other direction, let $a, b \in \mathbf{B}$ be such that $a/(p) \le
  b/(p)$. Then, by \cref{lemma:order},
  \[
    [a/(p)] \land \neg [b/(p)] = (a \land \neg b)/(p) = 0/(p),
  \]
  i.e.,
  \[
    a \land \neg b \in (p) \quad \iff \quad a \land \neg b \le p \quad \iff
    \quad a \land \neg b \land \neg p = 0
  \]
  by \cref{def:ideal,lemma:order}. Let us pick $a' = a \land \neg p$ and $b' = b
  \land \neg p$ since they satisfy $a'/(p) = a/(p)$ and $b'/(p) = b/(p)$ by
  \cref{lemma:elements_in_quotients}. It remains to show that $a \land \neg p
  \le b \land \neg p$. By \cref{lemma:order}, this is equivalent to $a \land
  \neg p \land \neg(b \land \neg p) = 0$. But
  \[
    a \land \neg p \land \neg(b \land \neg p) = a \land \neg p \land (\neg b
    \lor p) = (a \land \neg p \land \neg b) \lor (a \land \neg p \land p) = a
    \land \neg p \land \neg b,
  \]
  and we already have that $a \land \neg p \land \neg b = 0$ by assumption.
\end{proof}

% TODO: do I need this?
%\begin{corollary}
%  Let $I \subseteq \mathbf{B}$ be an ideal. If $\mathbf{B}$ is atomic, then so
%  is $\mathbf{B}/I$.
%\end{corollary}

@@

% TODO: how can WMC compute something in the quotient algebra?
% 1) The highlighted lemma from my notes.
% 2) the results about <=
% TODO: prove that the two ways to compute the probability give the same answer,
% i.e., how B(Delta) = B(L)/(not Delta).
% TODO: need an example of how we can compute probabilities in the quotient
% algebra.
% TODO: we can then move through the quotient BA using representatives we get
% from mapping true things to 1 and false things to 0.

>>>>

\begin{lemma}
  Let $(p)$ be a principal ideal. For any $a, b \in \mathbf{B}$, $a/(p) \le
  b/(p)$ if and only if $a \land \neg p \le b \land \neg p$.
\end{lemma}
\begin{proof}
  Let us begin with the `only of' direction. \Cref{lemma:elements_in_quotients}
  tells us that $(a \land \neg p)/(p) = a/(p)$. Combining this with
  \cref{lemma:canonical_homomorphism,lemma:homomorphisms_and_order} shows that
  \[
    a \land \neg p \le b \land \neg p \quad \implies \quad (a \land \neg p)/(p)
    \le (b \land \neg p)/(p) \quad \iff \quad a/(p) \le b/(p)
  \]
  as required.

  For the other direction, let $a, b \in \mathbf{B}$ be such that $a/(p) \le
  b/(p)$. Then, by \cref{lemma:order},
  \[
    [a/(p)] \land \neg [b/(p)] = (a \land \neg b)/(p) = 0/(p),
  \]
  i.e.,
  \[
    a \land \neg b \in (p) \quad \iff \quad a \land \neg b \le p \quad \iff
    \quad a \land \neg b \land \neg p = 0
  \]
  by \cref{def:ideal,lemma:order}. We need to show that $a \land \neg p \le b
  \land \neg p$. By \cref{lemma:order}, this is equivalent to $a \land \neg p
  \land \neg(b \land \neg p) = 0$. But
  \[
    a \land \neg p \land \neg(b \land \neg p) = a \land \neg p \land (\neg b
    \lor p) = (a \land \neg p \land \neg b) \lor (a \land \neg p \land p) = a
    \land \neg p \land \neg b,
  \]
  and we already have that $a \land \neg p \land \neg b = 0$ by assumption.
\end{proof}

@@

% TODO: how can WMC compute something in the quotient algebra?
% TODO: prove that the two ways to compute the probability give the same answer,
% i.e., how B(Delta) = B(L)/(not Delta).
% TODO: need an example of how we can compute probabilities in the quotient
% algebra.
% TODO: we can then move through the quotient BA using representatives we get
% from mapping true things to 1 and false things to 0.
